---
title: "Foxp2 Notebook"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
```

```{r lib, include=FALSE}
library(tidyverse)
library(xlsx)
library(skimr)
```


##Tactics:
There are two data sets to tidy and so we will approach each individually. First we will process the IOWA data set. 

##IOWA tidying:

Importing data:
```{r iowa_imp}
iowa <- read.xlsx("./data/IOWA_PLOS.xls", 1)
iowa <- as_tibble(iowa)
```

Rearranging the columns in the new dataset
```{r}
paired <- iowa %>% select(ID, everything())
```
 
##EXPLAINATION ON WHY WE UNITED ALL THESE POINTS


1) Merge rs7791396
```{r}
paired <- unite(data = paired, col = rs7791396, rs7791396_a1 , rs7791396_a2 , sep = '/' ) %>% 
  mutate(rs7791396 = as_factor(rs7791396))
```

2) Merge rs12155328
```{r}
paired <- unite(data = paired, col = rs12155328, rs12155328_a1 , rs12155328_a2 , sep = '/' ) %>% mutate(rs12155328 = as_factor(rs12155328))
```

3) Merge rs10447760
```{r}
paired <- unite(data = paired, col = rs10447760, rs10447760_a1 , rs10447760_a2 , sep = '/' ) %>% mutate(rs10447760 = as_factor(rs10447760))
```

4) Merge rs10953754
```{r}
paired <- unite(data = paired, col = rs10953754, rs10953754_a1 , rs10953754_a2 , sep = '/' ) %>% mutate(rs10953754 = as_factor(rs10953754))
```

5) Merge rs2244419
```{r}
paired <- unite(data = paired, col = rs2244419, rs2244419_a1 , rs2244419_a2 , sep = '/' ) %>% mutate(rs2244419 = as_factor(rs2244419))
```

5) Merge rs1668335
```{r}
paired <- unite(data = paired, col = rs1668335, rs1668335_a1 , rs1668335_a2 , sep = '/' ) %>% mutate(rs1668335 = as_factor(rs1668335))
```

6) Merge rs2396720
```{r}
paired <- unite(data = paired, col = rs2396720, rs2396720_a1 , rs2396720_a2 , sep = '/' ) %>% mutate(rs2396720 = as_factor(rs2396720))
```

7) Merge rs1916988
```{r}
paired <- unite(data = paired, col = rs1916988, rs1916988_a1 , rs1916988_a2 , sep = '/' ) %>% mutate(rs1916988 = as_factor(rs1916988))
```

8) Merge rs11505922
```{r}
paired <- unite(data = paired, col = rs11505922, rs11505922_a1 , rs11505922_a2 , sep = '/' ) %>% mutate(rs11505922 = as_factor(rs11505922))
```

9) Merge rs7785701
```{r}
paired <- unite(data = paired, col = rs7785701, rs7785701_a1 , rs7785701_a2 , sep = '/' ) %>% mutate(rs7785701 = as_factor(rs7785701))
```

10) Merge rs2106900
```{r}
paired <- unite(data = paired, col = rs2106900, rs2106900_a1 , rs2106900_a2 , sep = '/' ) %>% mutate(rs2106900 = as_factor(rs2106900))
```

11) Merge rs7799652
```{r}
paired <- unite(data = paired, col = rs7799652, rs7799652_a1 , rs7799652_a2 , sep = '/' ) %>% mutate(rs7799652 = as_factor(rs7799652))
```

12) Merge rs1005958
```{r}
paired <- unite(data = paired, col = rs1005958, rs1005958_a1 , rs1005958_a2 , sep = '/' ) %>% mutate(rs1005958 = as_factor(rs1005958))
```


Now that I painstakingly united the data lets look at it
```{r}
paired %>% glimpse()
```

#NOTICE THERE ARE ZEROES PRESENT. WE DO NOT THROW THEM OUT SINCE THE OBSERVATION CONTAINS OTHER USEFUL DATA JUST NOT USED IN ANALYSIS.



#ELVS DATA:
```{r elvs}
elvs <- read.xlsx("./data/ELVS_PLOS.xls", 1)
elvs <- as_tibble(elvs)
```


Rearranging the columns dropping the ID column. 
```{r}
tidy_elvs <- elvs %>% select(CELF7SS0, Call)
```



Lets investigate if there are any NA's
```{r}
tidy_elvs %>% skim()
```



There are 20 null values in the data set so I will remove them 
```{r}
tidy_elvs <- tidy_elvs %>% filter(!is.na(Call))
```


#RENAME THE CALL COLUMN TO REFLECT SNP






##Saving the data: 
#SAVE DATA HERE FOR BOTH.