---
title: "Table 4"
output: html_notebook
---

```{r libraries, include = FALSE}
library(tidyverse)
library(skimr)
library(knitr)
```


```{r read_in, include = FALSE}
elvs <- read_csv(here::here("data", "tidy_elvs.csv"))
elvs <- elvs %>% mutate(rs1916988 = as_factor(rs1916988))
iowa <- read_csv(here::here("data", "tidy_iowa.csv"))
iowa <- iowa %>% mutate_at(vars(starts_with("rs")), funs( as_factor(.)))
```

# RECODE STATEMENTS:


```{r shorthand}
# C start
CC <- 'C/C'
CG <- 'C/G'
CT <- 'C/T'

#G start
GG <- 'G/G'
GA <- 'G/A'
GT <- 'G/T'

#T start
TT <-  'T/T'
TC <- 'T/C'


#A start
AA <- 'A/A'
AC <- 'A/C'
AG <- 'A/G'


```
##rs7791396 recode
```{r rs779}
SNP_fact <-  iowa %>% mutate(rs7791396 = factor(rs7791396, levels = c(CC,CG,GG)))
SNP_fact %>% pull(rs7791396) %>% glimpse()
```

##rs12155328
```{r rs121}
SNP_fact <-  SNP_fact %>% mutate(rs12155328 = factor(rs12155328, levels = c(CC,CT,TT)))
SNP_fact %>% pull(rs12155328) %>% glimpse()
```

##rs10447760
```{r rs104}
SNP_fact <-  SNP_fact %>% mutate(rs10447760 = factor(rs10447760, levels = c(CC,CT,TT)))
SNP_fact %>% pull(rs10447760) %>% glimpse()
```


##rs10953754
```{r rs109}
SNP_fact <-  SNP_fact %>% mutate(rs10953754 = factor(rs10953754, levels = c(AA,AG,GG)))
SNP_fact %>% pull(rs10953754) %>% glimpse()
```


##rs2244419
```{r rs224}
SNP_fact <-  SNP_fact %>% mutate(rs2244419 = factor(rs2244419, levels = c(CC,CT,TT)))
SNP_fact %>% pull(rs2244419) %>% glimpse()
```



##rs1668335
```{r rs166}
SNP_fact <-  SNP_fact %>% mutate(rs1668335 = factor(rs1668335, levels = c(AA,GA,GG)))
SNP_fact %>% pull(rs1668335) %>% glimpse()
```


##rs2396720
```{r rs239}
SNP_fact <-  SNP_fact %>% mutate(rs2396720 = factor(rs2396720, levels = c(AA,AC,CC)))
SNP_fact %>% pull(rs2396720) %>% glimpse()
```


##rs1916988
```{r rs191}
SNP_fact <-  SNP_fact %>% mutate(rs1916988 = factor(rs1916988, levels = c(CC,TC,TT)))
SNP_fact %>% pull(rs1916988) %>% glimpse()
```

##rs11505922
```{r rs115}
SNP_fact %>% count(rs11505922) %>% glimpse() #used to formulate levels
SNP_fact <-  SNP_fact %>% mutate(rs11505922 = factor(rs11505922, levels = c(CC,CT,TT)))
SNP_fact %>% pull(rs11505922) %>% glimpse()
```


##rs7785701
```{r rs778}
SNP_fact %>% count(rs7785701) %>% glimpse() #used to formulate levels
SNP_fact <-  SNP_fact %>% mutate(rs7785701 = factor(rs7785701, levels = c(CC,CG,GG)))
SNP_fact %>% pull(rs7785701) %>% glimpse()
```

##rs2106900
```{r rs210}
SNP_fact %>% count(rs2106900) %>% glimpse() #used to formulate levels
SNP_fact <-  SNP_fact %>% mutate(rs2106900 = factor(rs2106900, levels = c(AA,GA,GG)))
SNP_fact %>% pull(rs2106900) %>% glimpse()
```

##rs7799652
```{r rs7799}
SNP_fact %>% count(rs7799652) %>% glimpse() #used to formulate levels
SNP_fact <-  SNP_fact %>% mutate(rs7799652 = factor(rs7799652, levels = c(GG,GT,TT)))
SNP_fact %>% pull(rs7799652) %>% glimpse()
```


##rs1005958
```{r rs100}
SNP_fact %>% count(rs1005958) %>% glimpse() #used to formulate levels
SNP_fact <-  SNP_fact %>% mutate(rs1005958 = factor(rs1005958, levels = c(CC,TC,TT)))
SNP_fact %>% pull(rs1005958) %>% glimpse()
```




Show the final product
```{r}
SNP_fact %>% glimpse()
```







#REPEAT TABLE 4!!!!

replicate call rates for iowa dataset 



Subsetting the data can making variables to be called.
```{r}
tot <- SNP_fact %>% count() %>% pull(n)

#subset long
long <- SNP_fact %>% filter(Sample == 'Longitudinal')
l_tot <- long %>% count() %>% pull(n)

#Subset school
sch <- SNP_fact %>% filter(Sample == 'School')
s_tot <- sch %>% count() %>% pull(n)

```


##rs7791396
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs7791396)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs7791396)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs7791396)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings! :)

##rs12155328
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs12155328)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs12155328)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs12155328)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs10447760
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs10447760)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs10447760)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs10447760)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs10953754
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs10953754)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs10953754)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs10953754)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings


##rs2244419
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs2244419)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs2244419)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs2244419)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings


##rs1668335
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs1668335)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs1668335)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs1668335)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs2396720
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs2396720)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs2396720)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs2396720)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs1916988
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs1916988)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs1916988)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs1916988)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs11505922
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs11505922)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs11505922)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs11505922)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs7785701
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs7785701)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs7785701)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs7785701)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Longitudinal is off by .01


##rs2106900
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs2106900)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs2106900)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs2106900)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs7799652
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs7799652)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs7799652)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs7799652)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings

##rs1005958
```{r}

t_call <- SNP_fact %>% filter(!is.na(rs1005958)) %>% count()
t_call <- signif(t_call/tot, 3)
l_call <- long %>% filter(!is.na(rs1005958)) %>% count()
l_call <- signif(l_call/l_tot,3)
s_call <- sch %>% filter(!is.na(rs1005958)) %>% count()
s_call <- signif(s_call/s_tot,3)

calls <- tibble('long' = c(l_call), 'school' =c(s_call),'comb'= c(t_call))

calls %>% glimpse()
```

Matches Previous Findings
